\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.3in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeText}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}
\begin{center}
    \textbf{\Huge Dea Satko} \\ \vspace{1pt}
    \small +44 7534827545 $|$ \href{mailto:dsatko+career@proton.me}{{dsatko+career@proton.me}} $|$ 
    \href{https://www.linkedin.com/in/deasatko/}{{linkedin.com/in/deasatko}} $|$
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Queen Mary University}{2020 -- 2021}
      {Master of Science: Accounting and Finance, Grade: Merit}{London, UK}
    \resumeSubheading
      {University of East London}{2017 -- 2020}
      {Bachelor of Arts: Accounting and Finance, Grade: First Class}{London, UK}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      {\textbf{\href{https://github.com/marex}{\faGithub} Borsa Italiana operational lifecycle} $|$ \emph{Marex Solutions}}{2023}
      \resumeText{Managed the full lifecycle of structured investment certificates—primarily capital-protected notes, credit-linked notes, fixed coupon notes, and Twin Win autocallable notes—on the Borsa exchange. Responsibilities included issuance, monitoring, and corporate actions, ensuring seamless market operations and final payments.}
      \resumeProjectHeading
      {\textbf{\href{https://github.com/marex}{\faGithub} Physical delivery of stocks} $|$ \emph{Marex Solutions}}{2022}
      \resumeText{Managed the physical settlement process, including stock delivery calculations and ensuring timely settlement with the clearer. Oversaw reconciliation, coordination with counterparties, and resolution of discrepancies to maintain efficient and accurate trade settlements.}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Marex Solutions}{2022 -- 2024}
      {Structured Products Operations Equity Analyst}{London, UK}
      \resumeItemListStart
        \resumeItem{Provided trading support, including pre- and post-sales assistance, trade capture, and coordination with paying agents and prime brokerage to ensure seamless execution.}
        \resumeItem{Managed the end-to-end physical settlement process, from calculating stock delivery requirements to ensuring timely settlement with clearing houses}
        \resumeItem{Oversaw the full lifecycle of structured product trades, including fixings, complex payoff calculations, monitoring triggers, and managing market shifts.}
        \resumeItem{Conducted trade, position, and cash reconciliations while calculating daily P\&L and Greeks to provide accurate risk assessments.}
        \resumeItem{Handled MiniFuture rolls, markdowns, expiries, knock-ins/outs, early terminations, and aggregations to maintain product integrity.}
        \resumeItem{Managed diverse asset classes, including bonds, equities, T-bills, forex, futures, TARFs, and structured products}
        \resumeItem{Administered corporate actions and equity assignments, ensuring accurate R-Factor adjustments and other event-driven changes.}
        \resumeItem{Produced and validated trade confirmations against legal agreements, ensuring compliance with contractual obligations.}
        \resumeItem{Adhered to operational risk frameworks, meeting FCA regulatory requirements and internal audit/compliance standards.}
        \resumeItem{Provided training and documented multiple procedures to ensure seamless handovers and operational continuity.}
      \resumeItemListEnd

   \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Finance}{: Structured Products Analysis and Pricing, Trading Book Reconciliation, Financial Modeling, Equity Research, Corporate Actions} \\
     \textbf{Softwares}{: Excel, Bloomberg, ICE Data Derivatives, Oracle PeopleSoft, Jira, Fireblocks and Coinbase} \\
     \textbf{Programming}{:\LaTeX} \\
     \textbf{Spoken Languages}{: English (Fluent), Italian (Native), Albanian (Native)}
    }}
 \end{itemize}

 %-----------ADDITIONAL INFORMATION-----------
\section{Additional Information}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
    {Studied Classical Piano for more than 10 years} \\
    {Attended Harvard Summer School (MA,USA) in 2009 to advance knowledge of the English language} \\
    {Squad Leader AGESCI BoyScout (IT), leading the team to win multiple challenges for 3 years consecutively} \\
    {Interests in videogames, travelling and gym}
   }} 
\end{itemize}

\end{document}